An Empirical Analysis of C Preprocessor Use

### 2000-01-18 macros/papers/emp-use-2.tex
OK, guys, I added the following paragraph just before the final paragraph (the roadmap) in Section 1:
"Through extensive discussions, we have found that experts have widely
varying experiences with the preprocessor and similarly varying
expectations about what our data should and do show.  Some of our
specific analyses could have been performed differently, and some can
be (and have been) interpreted in various ways.  Our data, however,
leave little doubt about our high-level views about the broad and
diverse usage of the preprocessor, about the majority of usages being
simple, nor about the p

>>>>

Through extensive discussions, we have found that experts have widely
varying experiences with the preprocessor and similarly varying
expectations about what our data should and do show.  Some of our
specific analyses could have been performed differently, and some can
be (and have been) interpreted in various ways.  Our data, however,
leave little doubt about our high-level views about the broad and
diverse usage of the preprocessor, about the majority of usages being
simple, nor about the potential for reducing at least some of the
complexity introduced by the more complicated uses.
